Outline

### 2017-07-21 Outline.Rmd
updated outline

### Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks

### Infrastructure provided to assist statistics educators
+ Take advantage of existing premium courses or build your own community course

@@

### High level description of technology
+ features of the design

### Comparison and contrast with competing technologies

### Explain why technology is innovative
+ Coding lesson / instructions are juxtaposed with practice window

### How to Create a DataCamp Community Course
+ What is needed to get started:  DataCamp account (verified instructor), GitHub
+ How to start building (including with collaborators)
+ Examples of DataCamp code for building different types of modules

>>>>

### Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks for understanding

### Infrastructure provided to assist statistics educators
+ Take advantage of existing courses or build your own community course
+ Tutorials on how to build courses
+ Links to some github repositories

@@

### High level description of technology / How to Create a DataCamp Community Course
+ What is needed to get started:  DataCamp account (verified instructor), GitHub
+ How to start building (including with collaborators)
+ Examples of DataCamp code for building different types of modules

### Comparison and contrast with competing technologies  
+ Swirl lessons
+ Anything else?

### Explain why technology is innovative
+ Coding lesson and instructions are juxtaposed with practice window, built in points and assessments to check for understanding, can integrate class with learning management systems
